iterSim

### 2023-02-08 analyses/complexSim.Rmd
checkpoint

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 2
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.5
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 10^-7
epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

@@

  # Evaluate the log cumulative hazard under the
  # Royston and Parmar specification
  res <-betas[["gamma0"]] * basis[[1]] + 
    betas[["gamma1"]] * basis[[2]] +
    betas[["gamma2"]] * basis[[3]] +
    betas[["gamma3"]] * basis[[4]] +
    betas[["gamma4"]] * basis[[5]] +
    betas[["z1"]] * x[["z1"]]+
    betas[["z2"]] * x[["z2"]]+
    betas[["z3"]] * x[["z3"]]+
    betas[["term1"]] * x[["z1"]]*x[["z2"]]*t+
    betas[["term2"]] * x[["z1"]]*x[["z3"]]+
    betas[["term3"]] * x[["z2"]]*(x[["z3"]])
  #
  # Return the log cumulative hazard at time t
  res
}
url<-'app.txt'
ds <- read.table(url, sep = '',header = TRUE)
ds$years.at.risk=pmin(ds$agein80,ds$onset)
brcancer$rectime<-brcancer$rectime/max(brcancer$rectime)
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1, data = brcancer, k = 3) #from flexsurv

# Simulate the event times
coefficients<-true_mod$coefficients
coefficients<-c(coefficients,z1=1,z2=1,z3=1,term1=10,term2=2,term3=2)

@@

@@

  #########################
  ###Simulate date
  #########################
  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5)))
  true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                       data = brcancer, k = 3
  ) #from flexsurv
  dat <- simsurv(betas = coefficients, # "true" parameter values
                 x = cov,                   # covariate data for 200 individuals
                 knots = true_mod$knots,    # knot locations for splines
                 logcumhazard = logcumhaz,  # definition of log cum hazard
                 maxt = 1,               # no right-censoring
                 interval = c(0,10000000)) # interval for root finding
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)

  #########################
  ###Simulate data
  #########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

  ###########################
  ###casebase optimal model
  ###########################
  final_mod_cb_glm <- fitSmoothHazard(status~bs(time)-time+z1+z2+z3+z1:z2:time+z1:z3+z2:z3,
                                      data = train,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

@@

  #########################
  ###casebase+splines
  #########################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI")

  glmAbsRisk<-as.data.frame(glmAbsRisk)

  rownames(glmAbsRisk)<-glmAbsRisk$time
  glmProper<- t(glmAbsRisk[-1,-1])

  class(glmProper)<-c("tunnel",class(glmProper))

  ######################
  ###PMNN splines
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=bsize,
                          verbose=0,
                          monitor="val_loss",
                          val_split=0.2,
                          min_delta=min_delta,
                          patience=patience)
  annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))

  ######################
  ###coxph
  ######################
  cox<-coxph(Surv(time, status) ~ z1+z2+z3, data = train,x=T)

  ######################
  ###DeepSurv
  ######################
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)
  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  ######################
  ###Deephit
  ######################
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ######################
  ###PMNN
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2),
                            name = 'main_input')

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status"
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=bsize,
                    verbose=0,
                    monitor="val_loss",
                    val_split=0.2,
                    min_delta=min_delta,
                    patience=patience)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly),
                             #'dsm'=dsmSurvProper) ,#'dsm'=dsmCleaned,
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

  saveRDS(BrierIPAList,'results/100hardBrier.rds')
  saveRDS(cScore,'results/100hardcidx.rds')
  pos<-pos+1
}

@@

>>>>

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 5
  iteration: 1
  layer1: 12
  layer2: 12
  layer3: 100
  layer4: 100
  drpt: 0.1
  lr: 0.01
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_support<-T
source_python('src/getSUP.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 10^-7

epo=as.numeric(params$epo)
patience <- as.numeric(params$patience)
iteration<-as.numeric(params$iteration)
layer1<-3*7#as.numeric(params$layer1)
layer2<-3*6#as.numeric(params$layer2)
layer3<-3*5#as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)
lr=as.numeric(params$lr)
paramTrials<-readRDS("complexTrials.rds") 
lr<-paramTrials[which.max(paramTrials$integBrier),]$lr
layer1<-paramTrials[which.max(paramTrials$integBrier),]$layer1
layer2<-paramTrials[which.max(paramTrials$integBrier),]$layer2
layer3<-3*5#as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-paramTrials[which.max(paramTrials$integBrier),]$drpt
bsize=paramTrials[which.max(paramTrials$integBrier),]$bsize
activ<-paramTrials[which.max(paramTrials$integBrier),]$actv

lr<-paramTrials[which.min(paramTrials$valLoss),]$lr
layer1<-paramTrials[which.min(paramTrials$valLoss),]$layer1
layer2<-paramTrials[which.min(paramTrials$valLoss),]$layer2
layer3<-3*5#as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-paramTrials[which.min(paramTrials$valLoss),]$drpt
bsize=paramTrials[which.min(paramTrials$valLoss),]$bsize
activ<-paramTrials[which.min(paramTrials$valLoss),]$actv

@@

  # Evaluate the log cumulative hazard under the
  # Royston and Parmar specification
  res <-betas[["gamma0"]] * basis[[1]] + 
    betas[["gamma1"]] * basis[[2]] +
    betas[["gamma2"]] * basis[[3]] +
    betas[["gamma3"]] * basis[[4]] +
    betas[["gamma4"]] * basis[[5]] +
    betas[["z1"]] * x[["z1"]]+
    betas[["z2"]] * x[["z2"]]+
    betas[["z3"]] * x[["z3"]]+
    betas[["term1"]] * x[["z1"]]*t*t+#*x[["z2"]]*
    betas[["term2"]] * x[["z1"]]*x[["z3"]]+
    betas[["term3"]] * x[["z2"]]*(x[["z3"]])
  #
  # Return the log cumulative hazard at time t
  res
}
url<-'app.txt'
ds <- read.table(url, sep = '',header = TRUE)
ds$years.at.risk=pmin(ds$agein80,ds$onset)
brcancer$rectime<-brcancer$rectime/max(brcancer$rectime)
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1, data = brcancer, k = 3) #from flexsurv

# Simulate the event times
coefficients<-true_mod$coefficients
coefficients<-c(coefficients,z1=0.05,z2=1.05,z3=1.05,term1=1.95,term2=1.05,term3=1.05)

@@

#########################
###Simulate date
#########################
  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,0,0.5),rnorm(numSamp/2,10,0.5)))
  true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                       data = brcancer, k = 3
  ) #from flexsurv

  dat <- simsurv(betas = coefficients, # "true" parameter values
                 x = cov,                   # covariate data for 200 individuals
                 knots = true_mod$knots,    # knot locations for splines
                 logcumhazard = logcumhaz,  # definition of log cum hazard
                 maxt = 10,               # no right-censoring
                 interval = c(0,10000000)) # interval for root finding
  colnames(dat)<-c("id","time","status")
  #samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  #dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]

  toDiv<-max(data$time)

  data$time<-data$time/toDiv
 spec = c(train = .7, test = .15, validate = .15)

 g = sample(cut(
   seq(nrow(data)), 
   nrow(data)*cumsum(c(0,spec)),
   labels = names(spec)
 ))

 res = split(data, g)

trainOG<-res$train

test<-res$test[,-c(ncol(data))]

fullTest<-res$test

val<-res$validate

numSamp<-nrow(trainOG)

@@

  #########################
  ###Simulate date
  #########################
  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,0,0.5),rnorm(numSamp/2,10,0.5)))
  true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                       data = brcancer, k = 3
  ) #from flexsurv
  dat <- simsurv(betas = coefficients, # "true" parameter values
                 x = cov,                   # covariate data for 200 individuals
                 knots = true_mod$knots,    # knot locations for splines
                 logcumhazard = logcumhaz,  # definition of log cum hazard
                 maxt = 10,               # no right-censoring
                 interval = c(0,10000000)) # interval for root finding
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.05))) #random censoring
  #dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)
  data<-data[,-1]
  data$time<-data$time/toDiv
  #########################
  ###Simulate data
  #########################
  #samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  #data<-data[,-1]
  #data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data

  sds<-sapply(train, function(x) (sd(x)))
means<-sapply(train, function(x) (mean(x)))
test<-normalizer(res$test,means,sds)[,-c(ncol(data))]
fullTest<-normalizer(res$test,means,sds)
val<-normalizer(res$validate,means,sds)

train<-normalizer(train,means,sds)
valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
valcb$offset<-0
valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
#val<-rbind(train,val)  
#test<-data[-samp,-c(ncol(data))]
  #fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 100
  )
  #times<-times[-c(1,length(times))]

  ###########################
  ###casebase optimal model
  ###########################
  final_mod_cb_glm <- fitSmoothHazard(status~bs(time)-time+z1+z2+z3+z1:time:time+z1:z3+z2:z3,
                                      data = train,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

@@

  #########################
  ###casebase+splines
 ##########################
    mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-as.data.frame(absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI"))
  rownames(glmAbsRisk)<-glmAbsRisk$time
  #prepare to run through riskRegression
  glmProper<- t(glmAbsRisk[-1,-1])
  class(glmProper)<-c("tunnel",class(glmProper))

  ######################
  ###PMNN splines
  ######################
    valcbtensor[[1]][[2]]<-rep(mod_cb_glm$offset[1],nrow(valcbtensor[[1]][[1]]))#
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = activ)%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = activ)%>%
    layer_dropout(drpt)%>%
    #layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    #layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate =lr )
  )

  fit<-fitSmoothHazSpline(pmnn,
                          epochs=epo,
                          batch_size=bsize,#floor(nrow(mod_cb_glm$data)/100),
                          verbose=0,
                          monitor="val_loss",
                          #val_split=0.2,
                          min_delta=min_delta,
                          patience=patience,val=valcbtensor)

   annPreds<-aarSplines(fit,
                       times=times,
                       x_test=test
  )
  rownames(annPreds)<-annPreds[,1]
  annProper<- t(annPreds[,-1])
  class(annProper)<-c("tunnel",class(annProper))
  rm(pmnn,fit,annPreds,covars_input,covars_output)
  ######################
  ###coxph
  ######################
  cox<-coxph(Surv(time, status) ~ z1+z2+z3, data = train,x=T)

  source_python('src/dsurv.py')
  #need to break ties
  tiebreakTrain<-train

  #while(length(unique(tiebreakTrain$time))/length(tiebreakTrain$time)!=1 ){
  #tiebreakTrain<-train
  #tiebreakTrain$time<-tiebreakTrain$time+runif(nrow(tiebreakTrain),0,1/10000000000)
  #}

  coxnnsurv=fitDeepSurv(tiebreakTrain,fullTest,floor(nrow(train)/100),epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
  coxnnsurv<-t(coxnnsurv)
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  # ######################
  # ###DeepSurv
  # ######################
  # coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
  #                 num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
  #                 early_stopping = TRUE, epochs = epo,
  #                 batch_size = bsize,device = "cpu",best_weights=T,
  #                 patience = patience,min_delta=min_delta,batch_norm = F,
  #                 learning_rate = 0.001,lr_decay=10^-7)
  # coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  # #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  # cnnCleaned<-pyProcess(coxnnsurv,times=times)
  # colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  # 
  ######################
  ###Deephit
  ######################
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,floor(nrow(train)/100),epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  ######################
  ###PMNN
  ######################

  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2),
                            name = 'main_input')

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = activ)%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = activ)%>%
    layer_dropout(drpt)%>%
    #layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    #layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = lr)
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=bsize,#floor(nrow(mod_cb_glm$data)/100),
                    verbose=0,
                    monitor="val_loss",
                    #val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=valcbtensor)
  annPreds<-aar(fit,
                times=times,
                x_test=test
  )

@@

  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score
    ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-1,1))
    rm(pmnn,fit,annPreds,covars_input,covars_output)
  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

@@

  saveRDS(BrierIPAList,'results/100hardBrier.rds')
  saveRDS(cScore,'results/100hardcidx.rds')
  pos<-pos+1
  gc()
}

@@

  ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()+coord_cartesian(ylim=c(-1,1))

```{r, learningTrial,eval=T}
  times<-seq(from=min(test$time)+0.000001,
             to=max(test$time)-0.000001,
             length.out = 25
  )

trials<-1000000
numTests<-2
# paramTrials<-data.frame(#lr=runif(trials,0,0.1),
#                         #drpt=runif(trials,0,0.5),
#                         lr=sample(c(0.0001,0.001,0.01,0.1),replace=T),
#                         drpt=sample(c(0.1,0.2,0.3,0.4),replace=T),
#                         layer1=sample(seq(10,71,20), trials,replace = T),
#                         layer2=sample(seq(10,71,20), trials,replace = T),
#                         #layer3=sample(seq(1,100,25), trials,replace = T),
#                         bsize=sample(c(floor(nrow(mod_cb_glm$data)/100),floor(nrow(mod_cb_glm$data)/100/2)), trials,replace = T),
#                         actv=sample(c("relu","tanh",'selu'), trials,replace = T),
#                         integBrier=rep(NA,trials))

paramTrials<-as.data.frame(tidyr::crossing(lr=c(0.001,0.01,0.1),
                        drpt=c(0.1,0.2,0.3),
                        layer1=seq(10,71,25),
                        layer2=seq(10,71,25),
                        bsize=c(floor(nrow(mod_cb_glm$data)/100)),
                        actv=c("relu","tanh"),
                        integBrier=NA,
                        valLoss=NA))
# 
# paramTrials<-unique.data.frame(paramTrials)
#paramTrials<-readRDS("complexTrials.rds")
for(i in 1:nrow(paramTrials)){
#paramTrials<-readRDS("complexTrials.rds")  
tempRes<-0
tempVal<-0
currentTime<-Sys.time() 
  for(j in 1:numTests){

  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2),
                            name = 'main_input')

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=paramTrials$layer1[i],use_bias = T,activation = paramTrials$actv[i])%>%
    layer_dropout(paramTrials$drpt[i])%>%
    layer_dense(units=paramTrials$layer2[i],use_bias = T,activation = paramTrials$actv[i])%>%
    layer_dropout(paramTrials$drpt[i])%>%
    #layer_dense(units=paramTrials$layer3[i],use_bias = T,activation = paramTrials$actv[i])%>%
    #layer_dropout(paramTrials$drpt[i])%>%
    #layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    #layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = paramTrials$lr[i])
  )

  fit<-fitSmoothHaz(pmnn,
                    epochs=epo,
                    batch_size=paramTrials$bsize[i],
                    verbose=0,
                    monitor="val_loss",
                    #val_split=0.2,
                    min_delta=min_delta,
                    patience=patience,val=valcbtensor)
  annPreds<-aar(fit,
                times=times,
                x_test=as.data.frame(val[,-c(ncol(data))])#rbind(train,val)
  )

  brierFinalResults <- Score(list('PMNN_Poly'=annProperpoly),
                             data =as.data.frame(val),#rbind(train,val) 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score
  cutted<-brierFinalResults[which(brierFinalResults$model=="PMNN_Poly"),]
  tempRes<-tempRes+mean(cutted[-c(1,2,24,25)]$IPA)/numTests
  tempVal<-tempVal+min(fit$resultOfFit$metrics$val_loss)/numTests
  }
  paramTrials$integBrier[i]<-tempRes
  paramTrials$valLoss[i]<-
  saveRDS(paramTrials,"complexTrials.rds")
  print(paste("trial",i))
  print(Sys.time()-currentTime)
  currentTime<-Sys.time()
  #print(as.character(paramTrials[i,]))
    rm(pmnn,fit,annPreds,covars_input,covars_output)

}
